A free/open-source Kazakh-Tatar machine translation system

### 2013-04-22 paper/paper.tex
various fixes

The paper will be laid out as follows: Section~\ref{sec:lang}\ gives a brief
description of the two languages; Section~\ref{sec:prev}\ gives a short review
of some previous work in the area of Turkic--Turkic language translation;
Section~\ref{sec:sys}\ describes the system and the tools used to construct it;
Section~\ref{sec:eval}\ gives a preliminary evaluation of the system; and
finally Section~\ref{sec:conc}\ describes our aims for future work and some
concluding remarks.

@@

Besides these systems, several previous works on making machine translation systems between Turkic languages 
exist, although to our knowledge none are publically available.
Some MT systems have been reported that translate between Turkish and other Turkic languages, 
including Turkish--Crimean Tatar \citep{altintas01},
Turkish--Azerbaijani \citep{hamzaoglu93}, Turkish--Tatar \citep{suleymanov08}, and
Turkish--Turkmen \citep{tantug07}, though none of these have been released to a public audience. The Turkish--Azerbaijani
pair is also available through Google Translate.\footnote{\url{http://translate.google.com}}

@@

For Tatar, the Tatar Wikipedia,\footnote{\url{http://tt.wikipedia.org/}; {\smallertt ttwiki-20130205-pages-articles.xml.bz2}} the New Testament in Tatar, and content from Radio Free Europe / Radio Liberty's Tatar-language service\footnote{\url{http://www.azatlyk.org/}} from early 2007 to early 2012.

>>>>

The paper will be laid out as follows: Section~\ref{sec:prev}\ gives a brief
description of the two languages; Section~\ref{sec:lang}\ gives a short review
of some previous work in the area of Turkic--Turkic language translation and compares the grammar of Kazakh and Tatar;
Section~\ref{sec:sys}\ describes the system and the tools used to construct it;
Section~\ref{sec:eval}\ gives a preliminary evaluation of the system; and
finally Section~\ref{sec:conc}\ describes our aims for future work and some
concluding remarks.

@@

Besides these systems, several previous works on making machine translation systems between Turkic languages 
exist, although to our knowledge none are publicly available except for the Turkish--Azerbaijani pair available through Google Translate.\footnote{\url{http://translate.google.com}}
Some MT systems have been reported that translate between Turkish and other Turkic languages, 
including Turkish--Crimean Tatar \citep{altintas01},
Turkish--Azerbaijani \citep{hamzaoglu93}, Turkish--Tatar \citep{suleymanov08}, and
Turkish--Turkmen \citep{tantug07}, though none of these have been released to a public audience.

@@

For Tatar, a dump of articles from the Tatar Wikipedia,\footnote{\url{http://tt.wikipedia.org/}; {\smallertt ttwiki-20130205-pages-articles.xml.bz2}} the New Testament in Tatar, and content from Radio Free Europe / Radio Liberty's Tatar-language service\footnote{\url{http://www.azatlyk.org/}} from early 2007 to early 2012 were used for testing.
